The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

  \subsection{The Galactic and Disk Models}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the interfaces between the disc and atmosphere are in thermal pressure equilibrium,\
  we can write the steady-state gaseous density distribution,\
  confined in the total potential, of the disc and  Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
     \text{, if $|z| < z_{0}$,}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disc-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the disc and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disc and atmosphere on the mid-plane $z=0$.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The density profile of the disc (red pluses) and\
             atmosphere (blue crosses) along the positive z-axis.\
             The density distribution is derived from hydrostatic equilibrium,\
             the interface ($z=0.1$) between the isothermal disc\
             and the atmosphere is pressure balanced.}
    \label{fig__initial-density-profile}
  \end{figure}

@@

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the atmosphere gas density by the peak density of\
  the smooth disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

>>>>

  \subsection{The Galactic and Disk Models}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by a plane-parallel potential that is symmetric about the mid-plane, or the Galactic plane, $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the interfaces between the isothermal disc and atmosphere are in thermal pressure equilibrium,\
  we can write the steady-state gaseous density distribution,\
  confined in the total potential, of the disc and  Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
     \text{, if $|z| < z_{0}$,}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disc-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disc and atmosphere on the mid-plane $z=0$.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The density profile of the isothermal disc (red pluses) and\
             atmosphere (blue crosses) along the positive z-axis.\
             The density distribution is derived from hydrostatic equilibrium,\
             the interface ($z=0.1$) between the isothermal disc\
             and the atmosphere is pressure balanced.}
    \label{fig__initial-density-profile}
  \end{figure}

@@

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the atmosphere gas density by the peak density of\
  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
